\bf Model Visualization Techniques for a Social Network Model

### 2017-02-24 paper.Rnw
average viz eperiments

To create a visualization that represents an ``average" network, we count occurences of each possible edge in the simulations, resulting in a summary network of simulations. Next, we subset the network to include

<<averagenet>>=
library(RSiena)
library(dplyr)
friend.data.w1 <- as.matrix(read.table("data/s50_data/s50-network1.dat"))
friend.data.w2 <- as.matrix(read.table("data/s50_data/s50-network2.dat"))
friend.data.w3 <- as.matrix(read.table("data/s50_data/s50-network3.dat"))
drink <- as.matrix(read.table("data/s50_data/s50-alcohol.dat"))
friendshipData <- array(c(friend.data.w1, friend.data.w2, friend.data.w3), dim = c(50, 50, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink)
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
M1sims1000 <- saom_simulate(dat = mydata, struct = M1eff,
                       parms = as.numeric(params), N = 1000)
M1avg <- net_avg(M1sims1000, 1)
@

>>>>

To create a visualization that represents an ``average" network, we count occurences of each possible edge in the simulations, resulting in a summary network of simulations. Next, we subset the network to include only those edges which appear in greater than 50\% of all

<<averagenet>>=
library(RSiena)
library(dplyr)
friend.data.w1 <- as.matrix(read.table("data/s50_data/s50-network1.dat"))
friend.data.w2 <- as.matrix(read.table("data/s50_data/s50-network2.dat"))
friend.data.w3 <- as.matrix(read.table("data/s50_data/s50-network3.dat"))
drink <- as.matrix(read.table("data/s50_data/s50-alcohol.dat"))
friendshipData <- array(c(friend.data.w1, friend.data.w2, friend.data.w3), dim = c(50, 50, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink)
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
library(netvizinf)
M1sims1000 <- saom_simulate(dat = mydata, struct = M1eff,
                       parms = as.numeric(params), N = 1000)
M1simsdf <- sims_to_df(M1sims1000)
M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
  group_by(from, to, wave) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))

library(geomnet)
M1avg$from <- paste0("n", M1avg$from)
M1avg$to <- paste0("n", M1avg$to)
M1avg2$from <- paste0("n", M1avg2$from)
M1avg2$to <- paste0("n", M1avg2$to)

library(tidyr)
M1avg[,-3] %>% spread(to, weight) %>% data.frame-> distmat
rownames(distmat) <- distmat$from
distmat <- distmat[,-1]
distmat <- as.matrix(1/distmat)
distmat[is.na(distmat)] <- 0
ggplot(data = M1avg %>% filter(weight/1000 > .5)) + # edge appears > 50% of the time. (is this actually what that is????) 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/1000), 
           directed = TRUE, curvature = .2,
           layout.alg = "fruchtermanreingold"
           #layout.alg = "kamadakawai",
           #layout.par = list(elen = distmat)
           )
ggplot(data = M1avg2 %>% filter(weight/1000 > .5)) + # edge appears > 50% of the time. (is this actually what that is????) 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/1000), 
           directed = TRUE, curvature = .2, labelon = T, labelgeom = 'label', labelcolour = 'white',
           layout.alg = "fruchtermanreingold"
           #layout.alg = "kamadakawai",
           #layout.par = list(elen = distmat)
           ) + 
  facet_wrap(~wave) + theme_net()
ggplot(data = M1avg %>% filter(weight >= 51)) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/500), 
           #directed = TRUE,
           layout.alg = "mds", 
           layout.par = list(var = 'user', dist = 'none', exp = 3,vm = distmat))

@
